Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-14 paper/main.tex
wrote main.tex...
update something

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Guizhou, China \\
benji.tong1117@gmail.com}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\subsection{Login}

\subsection{Imagery Overview}

The Resources on AWS is Light Every Night dataset of all VIIRS DNB and DMSP-OLS nighttime satellite data. Resource type is S3 Bucket. 
Amazon Resource Name (ARN) is arn:aws:s3:::globalnightlight. AWS Region is us-east-1. AWS CLI Access is no AWS account required, and 
command is "aws s3 ls s3://globalnightlight/ --no-sign-request" \cite{WorldBan13:online}.

@@

\subsection{Testing}

\subsection{Project management}

@@

\subsection{SiXiang Xiong}
\textbf{Role and Tasks:} BE, Testing

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
\textit{The University of Waikato}\\
Beijing, China \\
1561010}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Guizhou, China \\
benji.tong1117@gmail.com}
\and
\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
\IEEEauthorblockA{\textit{Faculty of Computer Sciences} \\
\textit{The University of Waikato}\\
Wuhan, China \\
1591686 sixianglearners3@gmail.com}
}

@@

\subsection{Login}
Springboot website adds third-party login Github login based on OAuth2
1. Introduction to OAuth2
OAuth is currently the most popular authorization mechanism used to authorize third-party applications and
obtain user data. OAuth has been widely used all over the world, and the current version 2.0. Simply put,
OAuth is an authorization mechanism. The owner of the data tells the system that they agree to authorize
third-party applications to enter the system and obtain these data. The system thus generates a short-term
entry token, which can be used in place of a password for use by third-party applications. Therefore.
the role of token and password is the same, both can enter the system, but these are three differences:
- The token is short-term, it will automatically expire when it expires and the user cannot modify it.
The password is generally valid for a long time and the user will not change if it is not modified.
- The token can be revoked by the data owner and will become invalid immidiately.
- The token has a scope, because the token has the same function as the password, the token must
also be kept strictly confidential. The consequences of leaking the token and leaking the password are
the same. This is why the validity period of the token is very short.
2. the principle of Github third-party login
Third-party login is actually OAuth authorization and authentication. The user wants to log into the
A website, and the A website allows the user to provide data from a third-party website to provide his
identity. Obtaining the identity data of a third-party website requires OAuth authorization.
Take the use of Github as a third-party login as an example:
The user clicks on the website to log in using Github, and the A website jumps to Github, callback
URI and Client ID will be brought:
1. Github asks the user to log in, and then asks "A website requires XX permmission, do you agree?"
For the same website, after agreeing once, user authorization is not required for logging in next time.
2. If the user agrees, Github will redirect back to website A and send back an authorization code.
3. A website uses the authorization code to request a token from Github.
4. Github returns the token.
5. Website A uses the token to request user data from Github.

\subsection{Imagery Overview}
The Resources on AWS is Light Every Night dataset of all VIIRS DNB and DMSP-OLS nighttime satellite data. Resource type is S3 Bucket. 
Amazon Resource Name (ARN) is arn:aws:s3:::globalnightlight. AWS Region is us-east-1. AWS CLI Access is no AWS account required, and 
command is "aws s3 ls s3://globalnightlight/ --no-sign-request" \cite{WorldBan13:online}.

@@

\subsection{Testing}
Use Postman testing tool to test this website. The security testing of Web application system have:
1. Catalogue configuration
set catalogue correctly, every catalogue should have index.html page or main.html page.
2. Login
Our system does not apply first-registe-last-login method, so hence that we does not need to test
valid and invalid username and password, the functionality of third-party login is able to help
us authorized our credential, only need to do the manual testing.
3. Session
Testing whether web application system have restriction of timeout. In other word, user need to
login again after 15 seconds if they have not clicked anything in this webpage then the website
logout or not.
4. Log file
For ensuring web application service security, log file is really essential, it must be test whether
relative information is write into log file and whether information can be tracked or not.
5. Encryption
While using safe socket, we need to test whether the encryption is correct and check the integrity
of the information.
6. Security vulnerabilities
Server-side scripts often constitute security vulnerabilities, and these vulnerabilities are often exploited by hackers.
Therefore, it is also necessary to test the problem that scripts cannot be placed and edited on the server side without authorization.
7. Code legality test
Code legality testing mainly includes two parts:
*program code legality test.
*display code legality test.
8. Documentation test
Integrity accurency consistency suitable reasonable relativity testability.
\subsection{Project management}

@@

\subsection{SiXiang Xiong}
\textbf{Role and Tasks:} BE, Testing
From my perspective, I have study many methods of writing user login and third party login,
finally learning how to implement the third party login with github as for our website,
usually we use OAuth2, springboot, then select java to develop, in this project, I help to test
this website though postman.
\textbf{Writing contribution includs:}
